`traveltime`: an R package to calculate walking and motorised travel time from user-specified locations

### 2025-02-06 paper/paper.qmd
replacing `travel_timesingapore` with `travel_time_singapore`
I cannot cope with the underscore then no space between words in one object name, sorry @njtierney

```{r}
#| label: calculate-result
travel_timesingapore <- calculate_travel_time(
  friction_surface = friction_singapore,
  points = stations
)

travel_timesingapore
```

We present the resulting calculated travel times in Figure \ref{fig-result}. Note that the results in `travel_timesingapore` include infinite (`Inf`) values. In Figure \ref{fig-data}, the islands to the south and north-east are shown as filled cells, but unconnected with the mainland. The raster cells for these islands appear absent in Figure \ref{fig-result}. Because they are not connected to any cells with a station, the calculated travel time is infinite, and so these cells do not appear in Figure \ref{fig-result}.

```{r}
#| label: fig-result
#| echo: false
#| fig-cap: "Map of walking travel time in Singapore, in minutes from 
#|   nearest MRT or LRT station."
ggplot() +
  geom_spatraster(
    data = travel_timesingapore
  ) +
  scale_fill_viridis_c(
    option = "A",
    direction = -1,
    na.value = "transparent"
  ) +
  theme_minimal() +
  labs(fill = "Minutes") +
  geom_spatvector(
    data = singapore_shapefile,
    fill = "transparent",
    col = "grey20"
  )
```

>>>>

```{r}
#| label: calculate-result
trave_time_singapore <- calculate_travel_time(
  friction_surface = friction_singapore,
  points = stations
)

trave_time_singapore
```

We present the resulting calculated travel times in Figure \ref{fig-result}. Note that the results in `trave_time_singapore` include infinite (`Inf`) values. In Figure \ref{fig-data}, the islands to the south and north-east are shown as filled cells, but unconnected with the mainland. The raster cells for these islands appear absent in Figure \ref{fig-result}. Because they are not connected to any cells with a station, the calculated travel time is infinite, and so these cells do not appear in Figure \ref{fig-result}.

```{r}
#| label: fig-result
#| echo: false
#| fig-cap: "Map of walking travel time in Singapore, in minutes from 
#|   nearest MRT or LRT station."
ggplot() +
  geom_spatraster(
    data = trave_time_singapore
  ) +
  scale_fill_viridis_c(
    option = "A",
    direction = -1,
    na.value = "transparent"
  ) +
  theme_minimal() +
  labs(fill = "Minutes") +
  geom_spatvector(
    data = singapore_shapefile,
    fill = "transparent",
    col = "grey20"
  )
```
